results notes

### 2022-09-05 RR_manuscript/results_notes.Rmd
♻️ - edit between-team variability section

```{r, 'load-meta-analysis'}

meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))

@@

compelling_count <- table(post_meta$compelling)

@@

<!-- TODO: discuss between-team variability -->

@@

- Analytic flexibility applies to us (as principal investigators) too.
- Research question was vague enough to possibily inflate between-team variability (REF, Hannah Fraser; although it is a typical kind of question, as found in the literature). We do relate analytical flexibility with underspecified hypothesis in the previous section.
- This should be replicated with a different question/data set.
- With this study, we can suggest that at a minimum this is the between-team variability, but need more studies like this one.
- Generalisability to linguistics/language sciences tout-court is limited. Need to do same with other fields, like language development, historical data, sociolinguistics, etc.
- The focus is on quantitative data analysis, so that we expect the issues raised here to apply differently or not at all to qualitative data analysis.
- We have not investigated researcher positionality, which is known to be an important factor.

>>>>

```{r load-meta-analysis}
meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))

@@

compelling_count <- table(post_meta$compelling)
```

@@

<!-- TODO: discuss between-team variability -->
<!-- TODO: This is more like between-model variability -->

As explained in the **Methods** section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e. the standard deviation of the group-level effect of team `(!!! we have now model_id)` returned by the meta-analytic model.

According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% confidence.
This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.

<!-- TODO: Add table with different outcomes, means (?) and SDs plus estimated deviations based on ±0.22/0.33 SDs. -->

@@

- Analytic flexibility applies to us (as principal investigators) too.
- Research question was vague enough to possibily inflate between-team variability (REF, Hannah Fraser; although it is a typical kind of question, as found in the literature). We do relate analytical flexibility with underspecified hypothesis in the previous section.
- This should be replicated with a different question/data set.
- With this study, we can suggest that at a minimum this is the between-team variability, but need more studies like this one.
- Generalisability to linguistics/language sciences tout-court is limited. Need to do same with other fields, like language development, historical data, sociolinguistics, etc.
- The focus is on quantitative data analysis, so that we expect the issues raised here to apply differently or not at all to qualitative data analysis.
- We have not investigated researcher positionality, which is known to be an important factor.
- Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did).
